Language Bias in a Multilingual Tweet Corpus

### 2018-06-21 paper.tex
Minor

@@

\author[A]{\fnms{Anonymous} \snm{Submission}%
\thanks{Corresponding Author: Book Production Manager, IOS Press, Nieuwe Hemweg 6B,
1013 BG Amsterdam, The Netherlands; E-mail:
bookproduction@iospress.nl.}}
%\author[B]{\fnms{Second} \snm{Author}}
%and
%\author[B]{\fnms{Third} \snm{Author}

%\runningauthor{B.P. Manager et al.}
\address[A]{Confidential Review Copy, Do Not Distribute}
%\address[B]{Short Affiliation of Second Author and Third Author}

@@

In addition to the location, 420 accounts were tracked.%\footnotemark{} %\hl{The whole list of screen names together with user ID is available in the supplement.}
%\footnotetext{In this paper, by ``tracking users'', we mean that their user IDs where passed to the Twitter API to collect tweets that they created, or the tweets that are replies by other users to their tweets. Refer to \url{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow} for a complete description. Keep in mind that this is different from the case when a user follows another user.}
%
The accounts are mostly Latvian (that is, coming from Latvia, but not necessary produce content in Latvian) news outlets, politicians, businesses, artists and sport clubs.

@@

To investigate the collection further, \hl{nine} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
\begin{itemize}
\item \texttt{LV001: Winter} Everything about winter.
\item \texttt{LV002: 
The Chronicles of Melanie} Mel\=anijas hronika (The Chronicles of Melanie) is a Latvian movie that was selected for Foreign-Language Category for Oscars.
\item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=ese\c{l}u putenis (Blizzard of Souls) that is currently in production.
\item \texttt{LV005: Ice hockey} Ice hockey related tweets.
\item \texttt{LV006: Christmas} Christmas.
\item \texttt{LV007: New Year} New Year.
\item \texttt{LV008: Olympics} Tweets about the Olympic games and the Latvian team.
\item \texttt{LV009: Brexit} Brexit.
\end{itemize}

>>>>

\newcommand{\sfile}[1]{\texttt{#1}}

@@

\author[A]{\fnms{Dmitrijs} \snm{Milajevs}%
  \thanks{Corresponding Author: Dmitrijs Milajevs, Guest Researcher,
    100 Bureau Drive,
    Gaithersburg, MD 20899, USA%
    ;
    E-mail: dmitrijs.milajevs@nist.gov.}}
%\author[B]{\fnms{Second} \snm{Author}}
%and
%\author[B]{\fnms{Third} \snm{Author}

\runningauthor{D. Milajevs}
\address[A]{Guest Researcher at National Institute of Standards and Technology, Maryland, USA}
%\address[B]{Short Affiliation of Second Author and Third Author}

@@

In addition to the location, 420 accounts were tracked.\footnotemark{} The accounts are mostly Latvian (that is, coming from Latvia, but not necessary produce content in Latvian) news outlets, politicians, businesses, artists and sport clubs. We avoided following personal accounts to respect their privacy. We also avoided bootstrapping the list, as it might have introduced accounts that originate outside of Latvia, for example, \sn{BBC}. The whole list of screen names together with user IDs is available in the supplement file \sfile{lv.cfg}.

\footnotetext{In this paper, by \hl{``tracking users''}, we mean that their user IDs where passed to the Twitter API to collect tweets that they created, or the tweets that are replies by other users to their tweets. Refer to \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{to the Twitter documentation} for a complete description. Keep in mind that this is different from the case when a user follows another user.}

@@

To investigate the collection further, \hl{nine} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
\begin{itemize}
\item \texttt{LV001: Winter} Everything about winter.
\item \texttt{LV002: 
The Chronicles of Melanie} Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for Foreign-Language Category for Oscars.
\item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is currently in production.
\item \texttt{LV005: Ice hockey} Ice hockey related tweets.
\item \texttt{LV006: Christmas} Christmas.
\item \texttt{LV007: New Year} New Year.
\item \texttt{LV008: Olympics} Tweets about the Olympic games and the Latvian team.
\item \texttt{LV009: Brexit} Brexit.
\end{itemize}
